Installation

### 2024-08-09 nbs/guides/installation.qmd
docs(nbs): note python 3.11 in installation guide
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```bash
echo "3.10" > .python-version
uv python install
uv venv -p 3.10
source .venv/bin/activate
uv pip install pyrovelocity
```

@@

```bash
alias mm=micromamba
mm create -n pyrovelocity python=3.10
mm activate pyrovelocity
mm install -c conda-forge pyrovelocity
```

>>>>

```bash
echo "3.11" > .python-version
uv python install
uv venv -p 3.11
source .venv/bin/activate
uv pip install pyrovelocity
```

@@

```bash
alias mm=micromamba
mm create -n pyrovelocity python=3.11
mm activate pyrovelocity
mm install -c conda-forge pyrovelocity
```
